Duration - Analysis for Non-Expressive performances

### 2020-05-06 material/analysis/stim_n/analysis/duration.Rmd
change file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
# read a filtered csv
dt_onset <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".")
dt_offset <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".")

>>>>

```{r extract, include = FALSE}
# read a filtered csv
dt_onset <- fread("../preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".")
dt_offset <- fread("../preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".")
